---
title: "final_report"
author: "Erika Canda"
date: "`r Sys.Date()`"
output:
 html_document:
  production: TRUE
---

The PAASIM project aims to conduct brief surveys to collect information on water sharing practices and household demographics.Results of this project will help inform on the status of water infrastructure in Mozambique and how it affects child and maternal health outcomes. Baseline surveys were conducted between 2019 and 2020 in households from neighborhoods across Beira.The goal of this preliminary analysis is to report household demographics data, and understand the relationship between independent variables such as education level and access to safely managed water through FIPAG, Mozambique's largest water supplier. 

```{r, read-config-list}

WHICH_CONFIG <-Sys.getenv("WHICH_CONFIG")
  config_list <- config::get(
    config = WHICH_CONFIG
)

```

```{r, set-chunk-opts, echo = FALSE, eval = config_list$production}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

# Descriptive Analysis
## Tabular analysis

```{r, load-data}

library(openxlsx)
library(here)
library(dplyr)
library(labelled)
        
here::i_am("final_report.Rmd")
stacked_data <- readRDS(
  file = here::here("output", "data_clean.rds")
)
```



```{r, table1}

table_one <- readRDS(
  file = here::here("output/table_one.rds")
)
table_one

```

Table 1: Demographic Characteristics Stratified by FIPAG Water Connection Status

This table presents a summary of demographic characteristics stratified by the status of FIPAG water connection. The data was collected at the household level, and included household who consented to be in the study. The demographic variables analyzed include sex, education level, number of household members, number of children under 5 in the household, pregnant women in the household, and pregnancy months. Statistical summaries such as counts, means, and percentages are provided for each variable, stratified by FIPAG water connection status. Significance of differences between groups is indicated by p-values. These findings offer insights into the distribution of demographic factors among individuals with and without access to FIPAG water connection, highlighting potential disparities in access to safely manages water infrastructure.

## Graphic Analysis Section

```{r, plot-data}
library (ggplot2)
library(janitor)
library(tidyr)

#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("output/bar_plot.png")
)
```


Figure 1: Distribution of Education Level by FIPAG Water Connection Status

This figure illustrates the distribution of education levels among households, grouped by their FIPAG water connection status. The education level variable indicates the highest educational attainment among household respondents.

